---
title: "Sagethemes"
author: "Sage Bionetworks"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
    code_fold: show
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---

# sagethemes

<!-- badges: start -->
[![R build status](https://github.com/Sage-Bionetworks/sagethemes/workflows/R-CMD-check/badge.svg)](https://github.com/Sage-Bionetworks/sagethemes/actions)
<!-- badges: end -->

The sagethemes package provides plot color palettes and themes that use the Sage
Bionetworks branded colors.

## Installation

```{r install, eval = FALSE}
remotes::install_github("Sage-Bionetworks/sagethemes", ref = "main")
```

## Colors

Colors were developed by the Sage design team and are available in the list
`sage_colors`.

```{r color-list}
library("sagethemes")
head(sage_colors, n = 3)
```

## Usage

sagethemes provides continuous, discrete, and binned scales. It also provides a
default theme, `theme_sage()`, which is currently just `theme_minimal()` but
with Lato as the font family and a larger default font size. Lato must be
installed for this theme to work. See the Fonts section below, and
`?import_lato` for more information.

```{r discrete}
library("ggplot2")
library("extrafont")
library("sagethemes")

# discrete
ggplot(mpg, aes(displ, hwy, colour = class)) +
  geom_point() +
  scale_color_sage_d() +
  theme_sage()
ggplot(mpg, aes(x = factor(year), fill = class)) +
  geom_bar() +
  scale_fill_sage_d() +
  theme_sage()
```

```{r continuous}
# continuous
ggplot(faithfuld, aes(waiting, eruptions, fill = density)) +
  geom_tile() +
  scale_fill_sage_c(option = "powder") +
  theme_sage()
```

```{r binned}
# binned -- note this requires ggplot2 version 3.3.1.9000 or greater
ggplot(faithfuld, aes(waiting, eruptions, fill = density)) +
  geom_tile() +
  scale_fill_sage_b(option = "powder") +
  theme_sage()
```

## Fonts

Sage Bionetworks uses [Lato](http://www.latofonts.com/lato-free-fonts/). If
you've installed Lato on your system, you should be able to use it in plots.

However, to output to PDF, PostScript, or bitmap files on Windows, you need to
register the font. sagethemes includes a copy of Lato, and you can load it with
`import_lato()`. If saving to PDF you'll also need to embed Lato in the PDF
file.

```{r lato, eval = FALSE}
import_lato()

p <- ggplot(mpg, aes(displ, hwy, colour = class)) +
  geom_point() +
  scale_color_sage_d() +
  theme_sage()

# Save PDF plot and embed Lato font
ggsave("plot.pdf", plot = p)
embed_fonts("plot.pdf", outfile = "plot_embed.pdf")
```

## Add logos

sagethemes allows you to add a logo to the bottom right of your plot with the
`logo_image()` and `logo_layout()` functions. By default it will use the Sage
Bionetworks logo, but you can also provide your own image, for example a
project-specific logo. This should be the last function call in your ggplot2
chain; you won't be able to add additional ggplot2 elements to the initial plot
after adding the logo.

```{r add-logo}
ggplot(mpg, aes(displ, hwy, colour = class)) +
  geom_point() +
  scale_color_sage_d() +
  theme_sage() +
  labs(
    title = "Gas mileage",
    subtitle = "Highway miles per gallon vs. engine displacement in liters"
  ) +
  logo_image() +
  logo_layout()
```

---

## Code of Conduct

Please note that the dccvalidator project is released with a [Contributor Code
of Conduct](.github/CODE_OF_CONDUCT.md). By contributing to this project, you
agree to abide by its terms.
