---
title: "Interacting with Synapse API"
author: "Sage Bionetworks"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
    code_fold: show
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Requirements

Set the value of `SYNAPSE_TOKEN` in the configuration file `.env` to one of your
Synapse personal access tokens. Token can be generated in Synapse via your User
Menu > Settings > Persona Access Tokens.

# Conda environments

List the Conda environments.

```{r}
library(reticulate)
options(reticulate.repl.quiet = TRUE)

conda_list(conda = "auto")
```

Activate the environment `sage-bionetworks`.

```{r}
use_condaenv("sage-bionetworks", required = TRUE)
```

# Logging into your Synapse account

```{r}
# Prepare Synapse Python Client
synapseclient <- reticulate::import('synapseclient')
syn <- synapseclient$Synapse()

# This Docker image creates the file ~/.synapseConfig with your credentials when
# the container starts so there is no need to specify the credentials here,
# hence preventing the risk of publishing this information to public Git
# repositories.
syn$login()
```

Upon successful logging, the message "Welcome, your name!" should be displayed
above.
